Failure Behaviour Analysis of Automated Pond Oxygen Management System

### 2015-02-19 IFIP FTA/manuscript.tex
cited

\section{Automatic Pond Oxygen Management System}
\label{sec:3}
An automated fault-tolerant pond oxygen management system is shown in Fig.\ref{fig5}. The role of this system is to automatically generate oxygen whenever the oxygen level of pond water starts falling. Broadly, this system has a power generation unit and two subsystems (subsystem 1 and 2). The power generation unit consists of an electricity generator and a main electricity supply line. In normal condition, the system is powered by the electricity from the main line. If the main line fails (disconnected or load-shedding) then the generator is enabled to provide electricity to the system. Subsystem 1 and 2 are identical because subsystem 2 is introduced to make the system fault-tolerant. 
%Subsystem 2 is a redundant block and works as a spare component for the system. If subsystem 1 fails then subsystem 2  takes over its tasks. 
Subsystem 1 has an oxygen level sensing block ${OSB}_1$. ${OSB}_1$ block has 2 oxygen dissolver sensor ${OS}_i \left(i=1,2\right)$. Each oxygen dissolver sensor ${OS}_i$ consists of a battery unit and a sensor. For simplicity, the battery unit and the sensor of the oxygen dissolver sensors are not shown in the figure. The oxygen level sensing block ${OSB}_1$ senses the oxygen level of the pond by using oxygen dissolver sensor ${OS}_1$ and sends the reading to the decision making block ${DM}_1 $. If  ${OS}_1$ fails then ${OS}_2$  performs the task of sensing. Therefore, ${OSB}_1$ can still operate if one of its sensors fails. Characteristics and functionality of ${OSB}_2$ are similar to that of ${OSB}_1$. Decision making block can decide whether to turn on an oxygen generator after getting the oxygen level reading from the ${OSB}_1$. If required ${DM}_1$ can turn on an oxygen generator from the oxygen generator block ${OGB}_1$. Failure of ${DM}_1$ would cause the subsystem 1 to fail because there is no spare component to take over its tasks. ${OGB}_1$ block has a dedicated (private) oxygen generator $\left({OG}_1\right)$ and a shared oxygen generator $\left({OG}_3\right)$. In normal condition, ${OG}_1$ is used to generate oxygen. If  ${OG}_1$fails then  ${OGB}_1$ can use ${OG}_3$ to generate oxygen. Similarly, if ${OG}_2$ of ${OGB}_2$ fails then ${OGB}_2$ can use ${OG}_3$ to generate oxygen.

>>>>

FTA has been widely used in different areas to perform both qualitative and quantitative dependability analysis of the systems. Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on. FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.  Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}. \textbf{The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
Elctornics system has used the FTA to study the behaviour of electronics system. Authors in [Microelectronics Reliability] uses FTA on printed circuit board assembly and 
for assessment of power system reliability [Reliability Engineering  System Safety]. The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  [Biological Invasions].} Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.

\section{Case Study: Automatic Pond Oxygen Management System}
\label{sec:3}
An automated fault-tolerant pond oxygen management system is shown in Fig.\ref{fig5}. The role of this system is to automatically generate oxygen whenever the oxygen level of pond water starts falling. Broadly, this system has a power generation unit and two subsystems (subsystem 1 and 2). The power generation unit consists of an electricity generator and a main electricity supply line. In normal condition, the system is powered by the electricity from the main line. If the main line fails (disconnected or load-shedding) then the generator is enabled to provide electricity to the system. Subsystem 1 and 2 are identical because subsystem 2 is introduced to make the system fault-tolerant. 
%Subsystem 2 is a redundant block and works as a spare component for the system. If subsystem 1 fails then subsystem 2  takes over its tasks. 
Subsystem 1 has an oxygen level sensing block ${OSB}_1$. ${OSB}_1$ block has 2 oxygen dissolver sensor ${OS}_i \left(i=1,2\right)$. Each oxygen dissolver sensor ${OS}_i$ consists of a battery unit and a sensor. For simplicity, the battery unit and the sensor of the oxygen dissolver sensors are not shown in the figure. The oxygen level sensing block ${OSB}_1$ senses the oxygen level of the pond by using oxygen dissolver sensor ${OS}_1$ and sends the reading to the decision making block ${DM}_1 $. If  ${OS}_1$ fails then ${OS}_2$  performs the task of sensing. Therefore, ${OSB}_1$ can still operate if one of its sensors fails. Characteristics and functionality of ${OSB}_2$ are similar to that of ${OSB}_1$. Decision making block can decide whether to turn on an oxygen generator after getting the oxygen level reading from the ${OSB}_1$. If required ${DM}_1$ can turn on an oxygen generator from the oxygen generator block ${OGB}_1$. Failure of ${DM}_1$ would cause the subsystem 1 to fail because there is no spare component to take over its tasks. ${OGB}_1$ block has a dedicated (private) oxygen generator $\left({OG}_1\right)$ and a shared oxygen generator $\left({OG}_3\right)$. In normal condition, ${OG}_1$ is used to generate oxygen. If  ${OG}_1$fails then  ${OGB}_1$ can use ${OG}_3$ to generate oxygen. Similarly, if ${OG}_2$ of ${OGB}_2$ fails then ${OGB}_2$ can use ${OG}_3$ to generate oxygen.
